Comparison with Christensen paper

### 2018-12-14 paper-comparison/compare-christensen.Rmd
note diagnose argument
Add LDA comparisons
LDATS chooses 6 topics but the paper had 4.

## Christensen 2018 analysis

@@

@@

ldats_dat <- ch_dat
rodents$document_term_table <- ch_dat

@@

>>>>

## Christensen 2018 analysis files

@@

I added an argument 'diagnose' to the create_rodent_table() function. If T, returns the raw table & # of plots tables as well as the adjusted table.

@@

ldats_dat <- as.matrix(ch_dat)
ldats_dat <- apply(ldats_dat, c(1,2), FUN = as.integer)
rodents$document_term_table <- ldats_dat
rm(ldats_dat)
rm(ldats_dates)

@@

## LDA

While LDATS can run start-to-finish with `LDATS::LDA_TS`, I'm first going to step through function-by-function to isolate differences with the paper.

```{r LDATS LDAs}

ldats_ldas <- LDATS::LDA_set(document_term_table = rodents$document_term_table, topics = c(2:6), nseeds = 100)
ldats_lda_selected <- LDATS::select_LDA(LDA_models = ldats_ldas)

Paper LDAS:

```{r paper LDAs}
source('christensen-ecology-files/AIC_model_selection.R')
source('christensen-ecology-files/LDA-distance.R')

# Fit a bunch of LDA models with different seeds
# Only use even numbers for seeds because consecutive seeds give identical results
seeds = 2*seq(200)

# repeat LDA model fit and AIC calculation with a bunch of different seeds to test robustness of the analysis
best_ntopic = repeat_VEM(ch_dat,
                         seeds,
                         topic_min=2,
                         topic_max=6)
hist(best_ntopic$k,breaks=c(0.5,1.5,2.5,3.5,4.5,5.5,6.5,7.5,8.5,9.5),xlab='best # of topics', main='')

# 2b. how different is species composition of 4 community-types when LDA is run with different seeds?
# ==================================================================
# get the best 100 seeds where 4 topics was the best LDA model
seeds_4topics = best_ntopic %>% 
  filter(k == 4) %>% 
  arrange(aic) %>% 
  head(100) %>% 
  pull(SEED)

# choose seed with highest log likelihood for all following analyses
#    (also produces plot of community composition for 'best' run compared to 'worst')
best_seed = calculate_LDA_distance(ch_dat,seeds_4topics)
mean_dist = unlist(best_seed)[2]
max_dist = unlist(best_seed)[3]

# ==================================================================
# 3. run LDA model
# ==================================================================
ntopics = 4
SEED = unlist(best_seed)[1]  # For the paper, I use seed 206
ldamodel = LDA(ch_dat,ntopics, control = list(seed = SEED),method='VEM')

```{r plot LDAs}
# Paper
LDA_plot_top_panel(ldamodel, cols = NULL, option = "D")

# LDATS
LDA_plot_top_panel(ldats_lda_selected[[1]], cols = NULL, option = "D")
```

## Changepoint
